Highlights of NIPS 2016

### 2017-01-15 Highlights/slides.tex
[major] final final version of slides for highlights presentation

@@

    \begin{figure}
      \centering
      \includegraphics[width=0.8\textwidth]{rnn1.png}
    \end{figure}

    \footnotetext[1]{}
  \end{frame}

  \begin{frame}
    \frametitle{RNN: Symposia}

    %\footnotetext[1]{}
  \end{frame}

  \begin{frame}
    \frametitle{RNN: Applications}

    %\footnotetext[1]{}
  \end{frame}

@@

  \begin{frame}
    \frametitle{Learning to learn: Meta-learning}

    %\footnotetext[1]{}
  \end{frame}

@@

    %\footnotetext[1]{}
  \end{frame}

  \subsection{Neural Turing Computers}

  \begin{frame}
    \frametitle{Neural Turing Machines: Overview}

    %\footnotetext[1]{}
  \end{frame}

  \begin{frame}
    \frametitle{NTM: Applications}

    %\footnotetext[1]{}
  \end{frame}

  \begin{frame}
    \frametitle{Nuts and Bolts of ML}

    %\footnotetext[1]{}
  \end{frame}

  \begin{frame}
    \frametitle{General AI: Unsupervised Learning}

    %\footnotetext[1]{}
  \end{frame}

@@

    %\footnotetext[1]{}
  \end{frame}

  \begin{frame}
    \frametitle{Efficient seeding for K-Means}

    %\footnotetext[1]{}
  \end{frame}

@@

    %\footnotetext[1]{}
  \end{frame}

  \section{Visitng Barcelona}

@@

  \end{frame}

@@

    \begin{center}
      \Huge{Thank you!}\\~\\
      \huge{Questions or Comments?}
    \end{center}
  \end{frame}

>>>>

  \begin{frame}
    \frametitle{Nuts and Bolts of ML: Andrew Ng}

    \begin{itemize}
      \item Practical advice on machine learning research
      \item Importance of human-level accuracy as metric
      \item Techniques for collecting data to train models.
    \end{itemize}

    \begin{figure}
      \centering
      \includegraphics[width=0.8\textwidth]{ngKeynote.jpg}
    \end{figure}

    \footnotetext[1]{https://www.youtube.com/watch?v=F1ka6a13S9I}
  \end{frame}

  \begin{frame}
    \frametitle{Predictive Learning: Yann Lecun}

    \begin{figure}
      \centering
      \caption*{General AI means agents should have \textbf{Common Sense}\footnotemark[1]}
      \includegraphics[width=0.8\textwidth]{generalAI2.png}
    \end{figure}

    \footnotetext[1]{\url{https://nips.cc/Conferences/2016/Schedule?showEvent=6197}}
  \end{frame}

  \begin{frame}
    \frametitle{Predictive Learning: Yann Lecun}

    \begin{figure}
      \centering
      \caption*{Key to General AI will be \textbf{Unsupervised Learning}\footnotemark[1]}
      \includegraphics[width=0.8\textwidth]{generalAI1.png}
    \end{figure}

    \footnotetext[1]{\url{https://nips.cc/Conferences/2016/Schedule?showEvent=6197}}
  \end{frame}

  \begin{frame}
    \frametitle{Intelligent Biosphere: Drew Purves}

    \begin{figure}
      \centering
      \caption*{Intelligent life strongly depends on the environment and vice versa\footnotemark[1]}
      \includegraphics[width=0.8\textwidth]{generalAI4.png}
    \end{figure}

    \footnotetext[1]{\url{https://nips.cc/Conferences/2016/Schedule?showEvent=6193}}
  \end{frame}

  \begin{frame}
    \frametitle{Learning from the Brain: Saket Navlakha}

    \begin{figure}
      \centering
      \caption*{Pruning of neural connections is crucial for Learning in Brain\footnotemark[1]}
      \includegraphics[width=0.8\textwidth]{generalAI3.png}
    \end{figure}

    \footnotetext[1]{https://nips.cc/Conferences/2016/Schedule?showEvent=6192}
  \end{frame}

@@

    \begin{figure}
      \centering
      \includegraphics[width=0.7\textwidth,height=0.45\textheight]{rnn2.png}
    \end{figure}

    \footnotetext[1]{http://papers.nips.cc/paper/6114-weight-normalization-a-simple-reparameterization-to-accelerate-training-of-deep-neural-networks}
    \footnotetext[2]{https://arxiv.org/pdf/1611.02779.pdf}
    \footnotetext[3]{http://papers.nips.cc/paper/6310-phased-lstm-accelerating-recurrent-network-training-for-long-or-event-based-sequences}
  \end{frame}

@@

  \begin{frame}
    \frametitle{Learning to (learn by gradient descent) by gradient descent}

    \begin{itemize}
      \item Current optimizers are parametric and domain specific.
      \item Attempt to learn the optimizer using RNN.
    \end{itemize}
    \begin{equation}
      \theta_{t+1} := \theta_t + g(\Delta f(\theta_t), \phi)
    \end{equation}

    \begin{figure}
      \centering
      \includegraphics[width=0.9\textwidth]{metalearning1.png}
    \end{figure}

    \footnotetext[1]{Andrychowicz et al., ``Learning to learn by gradient descent by gradient descent'' in \emph{NIPS 2016}}
  \end{frame}

@@

    \begin{itemize}
      \item Novel architectures proposed for one-shot learning.
      \item The idea is a differentiable nearest neighbor classifier.
    \end{itemize}

    \begin{figure}
      \centering
      \includegraphics[width=0.8\textwidth]{oneshot1.png}
    \end{figure}

    \footnotetext[1]{Vinyals et al., ``Matching networks for one shot learning'' in \emph{NIPS 2016}}
  \end{frame}

  \subsection{Differentiable Neural Computers}

  \begin{frame}
    \frametitle{Differentiable Neural Computers}

    \begin{itemize}
      \item Neural Network with memory access (Read, Write, Link).
      \item Used for skill transfer, reinforcement learning, reasoning etc.
    \end{itemize}

    \begin{figure}
      \centering
      \includegraphics[width=0.8\textwidth]{dnc.png}
    \end{figure}

    \footnotetext[1]{https://deepmind.com/blog/differentiable-neural-computers/}
  \end{frame}

  \section{Other Topics}

@@

    \begin{center}
      \href{run:./Videos/BostonDyn.avi?loop}{\includegraphics[width=0.9\textwidth]{./Videos/BostonDyn.png}}
    \end{center}

    \footnotetext[1]{https://nips.cc/Conferences/2016/Schedule?showEvent=6194}
  \end{frame}

  \begin{frame}
    \frametitle{Classic Algorithms: KMeans and Matrix Completion}

    \begin{itemize}
      \item Matrix completion: Non-convex objective for matrix completion has no spurious local minima \footnotemark[1]
      \item Clustering: Seedings for large-scale k-means++ clustering \footnotemark[2]
    \end{itemize}

    \begin{figure}
      \centering
      \includegraphics[width=0.9\textwidth]{kmeans.png}
    \end{figure}

    \footnotetext[1]{http://papers.nips.cc/paper/6048-matrix-completion-has-no-spurious-local-minimum}
    \footnotetext[2]{http://papers.nips.cc/paper/6478-fast-and-provably-good-seedings-for-k-means}
  \end{frame}

@@

    \centering Prank by NIPS organizers to warn about the AI Bubble

    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{rocketai2.png}
    \end{figure}

    \footnotetext[1]{\url{https://medium.com/the-mission/rocket-ai-2016s-most-notorious-ai-launch-and-the-problem-with-ai-hype-d7908013f8c9}}
  \end{frame}

@@

    \begin{columns}
      \begin{column}{0.5\textwidth}
        \begin{figure}
          \centering
          \includegraphics[width=\textwidth]{barc3.jpeg}
        \end{figure}
      \end{column}
      \begin{column}{0.25\textwidth}
        \begin{figure}
          \centering
          \includegraphics[width=\textwidth]{barc1.jpeg}
        \end{figure}
      \end{column}
      \begin{column}{0.25\textwidth}
        \begin{figure}
          \centering
          \includegraphics[width=\textwidth]{barc2.jpeg}
        \end{figure}
      \end{column}
    \end{columns}
  \end{frame}

@@

    \begin{center}
      \Huge{Thank you!}\\~\\
      \huge{Take home Messages}
      \normalsize
      \begin{itemize}
        \item Deep Learning is no longer just a tool!
        \item Emphasis is changing to General AI and Life long learning
        \item Recurrent Neural Networks are very important!
      \end{itemize}
    \end{center}
  \end{frame}
